---
title: "Income and Ideology"
author: "Your Name Here"
date: "April 13, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(primer.data)
library(tidyverse)
library(rstanarm)
library(tidybayes)
library(ggdist)

# Check out the raw cces tibble, especially the faminc (family income) and
# ideology variables.

x <- cces %>% 
  filter(year == 2019) %>% 
  select(state, gender, age, race, faminc, ideology) %>% 
  drop_na() %>% 
  
  # This is an absurd hack. Do not do this, ever. This only works because, if
  # you coerce factor variables into integers, the order of the factor levels is
  # preserved. So, low numbers for faminc/ideology correspond to poorer/liberal
  # individuals.
  
  # We need the variables, at least faminc, to be numeric so that we can create
  # a statistical model using the tools we have learned.
  
  mutate(faminc = as.integer(faminc)) %>% 
  mutate(ideology = as.integer(ideology))

  
```


*Describe the relationship between ideology and family income. How does it vary by gender? Does your conclusion change if we "adjust" for race and age?*


## Wisdom
- data is from the US 2006 - 2019
- we have info for all variables (ideology, family income, gender, race, age)

x %>%
ggplot(aes(faminc, ideology)) +
geom_jitter(alpha = 0.05) +
geom_smooth(formula = y ~ x,
            method = "lm")


## Justice
step one is to ask, what is the form of the model? is this a linear or logistic model? 


```{r fit_1}

fit_1 <- stan_glm(formula = ideology ~ faminc,
                  data = x,
                  refresh = 0,
                  seed = 334)
                  
                  
print(fit_1, details = FALSE, digits = 3)

```

As family income increases, the ideology decreases slightly (becomes more liberal)

here's our formula:

$$ideology_i = \beta_0  + \beta_1 faminc + \epsilon_i$$
beta0: when income is 0, ideology is 3.74 (left of center)
beta1: slope, predictive claim: when comparing two different families, the one that's richer is going to be a bit more liberal (by a margin of .047)

note: if there hasn't been an experiment, we should be careful about making causal claims



```{r fit 2}

fit_2 <- stan_glm(formula = ideology ~ faminc + gender + faminc*gender,
                  data = x,
                  refresh = 0,
                  seed = 222)

print(fit_2, details = FALSE, digits = 3)

```


$$ideology_i = \beta_0  + \beta_1 faminc + \beta_2 gender + \beta_3 faminc*gender + \epsilon_i$$

```{r fit_3}

fit_3 <- stan_glm(data = x,
                  ideology ~ age + race + gender +faminc + gender*faminc,
                  refresh = 0,
                  seed = 39)


print(fit_3, details = FALSE, digits = 3)

```


```{r plot}
age <- 50
race <- c("White", "Black")
gender <- c("Male", "Female")
faminc <- c(1, 6, 12)

newobs <- expand_grid(age, race, gender, faminc)

z <- add_fitted_draws(newobs, fit_3) %>%
  mutate(faminc = factor(faminc, levels = c(1, 6, 12)))

z %>%
  ggplot(aes(x = .value,
             y = faminc,
             fill = gender)) +
  
  stat_slab(alpha = 0.5)

# check the repo for updated content here 





# ignore this warning 

```



## Courage


## Temperance

